Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)

### 2015-10-14 supportingInformation.tex
terminada revisao das figuras
comecando revisao do SI

\newcommand{\beginsupplement}{%
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information)}% Force line breaks with \\

@@

The supporting information (this document) contains statistics for time activity (circular statistics and histograms) in Section~\ref{sec:time}, the fraction of vertices in the peripheral, intermediary and hub sectors in Section~\ref{si:frac} and the combination of basic topological measures into principal components with greater variance in Section~\ref{si:pcat}. There is a focus on email list interaction networks for benchmarking and
Section~\ref{si:ext} reinforces the results with the analysis of networks from Facebook, Twitter and Participa.br.
More context (e.g. methods, discussion, data and scripts) is given in the main document~\cite{tpaper}.

\section{Time activity in different scales}\label{sec:time}
Here we complement the theory presented in Section~\ref{sec:mtime} and results in Section~\ref{constDisc} of the paper~\cite{tpaper}.

\subsection{Time circular measures}\label{si:circ}
The measurements used were the rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence $\frac{max(incidence)}{min(incidence)}$ at each time unit.
Also, $ \mu_{\frac{max(incidence')}{min(incidence')}} $ and $ \sigma_{\frac{max(incidence')}{min(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples. Greater dispersion is found on seconds and minutes, followed
by days of the month. Greater localization if found in the hours of the day, followed by weekdays and months.

>>>>

\newcommand{\beginsupplement}{%
%	\setcounter{table}{0}
	\renewcommand{\thesection}{S\Roman{section}}%
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)}% Force line breaks with \\

@@

This Supporting Information document holds circular statistics and histograms of activity along time in Section~\ref{sec:time},
the fraction of vertices in the peripheral, intermediary and hub sectors in Section~\ref{si:frac}
and the combination of basic topological measures into principal components with greater variance in Section~\ref{si:pcat}.
There is a focus on email list interaction networks for benchmarking and
Section~\ref{si:ext} reinforces the results with the analysis of networks from Facebook, Twitter and Participa.br.
More context (e.g. methods, discussion, data and scripts) is given in the main document~\cite{tpaper}
to which this current document supplies supporting information.

\section{Time activity in different scales}\label{sec:time}
This section presents information derived from the theory presented in Section~\ref{sec:mtime}
for supporting the results in Section~\ref{constDisc}.

\subsection{Time circular measures}\label{si:circ}
The measurements used were the rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of the minimum and the maximum incidences $\frac{min(incidence)}{max(incidence)}$ at each time scale.
Also, $ \mu_{\frac{min(incidence')}{max(incidence')}} $ and $ \sigma_{\frac{min(incidence')}{max(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples.
Greater dispersion is found on seconds and minutes, followed
by days of the month.
Greater localization if found in the hours of the day, followed by weekdays and months.
